Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-21 paper/paper.tex
pass on fuzzing

\begin{table}[t]
  \small
  \setlength{\tabcolsep}{4.5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 137 & 47 & 323 & 21 & 483 \\
    \quickfuzz{} & 81 & 62 & 349 & 13 & 369 \\
    \midrule
    \textbf{total} & 218 & 109 & 672 & 34 & 852 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 9 \\
    & Timeout/OME & 28 & 13 \\
    & * Invalid Input & 39 & 48 \\    
    & * Error Message Mismatch & 41 & 12 \\
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \small
  \setlength{\tabcolsep}{4.5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
    \midrule
    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 9 \\ % 26 & 9 
    & Timeout/OME & 28 & 13 \\ % 28 & 13
    & * Invalid Input & 39 & 48 \\ % 39 & 48
    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\ % 34 & 28
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}
